%!TEX root = ../cv.tex
\cvsection{Projects}


\cvsubsection{External projects}

\begin{cventries}

\cventry
  {Developer}
  {TeleForm}
  {Barcelona, Spain}
  {Jul. 2016}
  {
    A project developed for the Typeform Summer Hackathon. The project consisted of
    developing a Telegram Bot which implemented forms using the TypeForm IO API\@.
    The project was awarded the \textit{Most Creative} implementation idea
    by the engineers from TypeForm.
    [\href{https://github.com/albertomontesg/typeformHack}{Code}]
  }

\end{cventries}

\filbreak

\cvsubsection{School-Related Projects}

\begin{cventries}

\cventry
  {Researcher}
  {Fast 2D $N^2$ t-distributed Stochastic Neighbor Embedding}
  {ETH Z\"urich, Switzerland}
  {Feb. 2017 - Jun. 2017}
  {
    The project presents a faster implementation of the $N^2$ t-SNE embedding.
    This version is restricted to producing 2D output vectors and has been
    developed for CPU architectures supporting AVX2 instructions.
    It also analyses performance blockers and elevate them by increasing
    locality and hand-optimizing the code.
    The project implementation yields the fastest implementation known to the
    t-SNE authors.
    The project was performed in teams for the course
    \textit{How to Write Fast Numerical Code} at ETHZ.
    [\href{https://github.com/albertomontesg/fast-tsne}{Code}]
  }

\cventry
  {Processing Team Leader}
  {RADiCal (Radar Technologies for Smart Cities)}
  {UPC Barcelona, Spain}
  {Feb. 2015 - Jun. 2015}
  {
    The project was done by a group of 20 engineering students in the design
    and development of a radar-based system for monitoring and surveilling
    traffic conditions, pedestrian density and parking availability in a city.
    The project was part of a university semester course with an on-site
    dedication of 8 hours per week. My role in this project was the Team Leader
    of the Processing Team responsible for the signal processing and the server
    infrastructure to manage all the data gathered by the radar.
  }

\cventry
  {Developer}
  {Project Lightning Streaming}
  {UPC Barcelon, Spain}
  {Feb. 2013 - Jun. 2013}
  {
    University course project performed in teams. The goal of the project was
    the creation of an app for Android which could be able to connect to a
    server and watch videos in streaming using HTTP Live Streaming protocol.
    [\href{https://github.com/albertomontesg/LightningStreaming}{Code}]
  }

\cventry
  {Researcher}
  {Electromagnetism and Magnetic Levitation}
  {Barcelona, Spain}
  {Sep. 2010 - Feb. 2011}
  {
    High school research project. The project consisted of studying the magnetic
    levitation using Foucault currents performing some experimentation and
    mathematical analysis.
    It was given the highest grade as well as an award by the Catalan
    Government.
  }

\end{cventries}
