%!TEX root = ../cv.tex
\cvsection{Research}

\begin{cventries}

\cventry
	{Bachelor Thesis}
  {Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks}
	{Barcelona, Spain}
	{Feb. 2016 - Jul. 2016}
  {
    \begin{cvitems}
    \item{
      The thesis explores the use of Convolutional Neural Networks and Recurrent
      Neural Networks to classify activities in videos and temporally localize
      this activities.}
    \item{
      Participated in \emph{ActivityNet Large Scale Activity Recognition
      Challenge} at CVPR 2016.}
		\item{The work was presented at \emph{NIPS 2016 Workshop LSCVS} winning the
		  \emph{Best Poster} award.
      \href{https://imatge-upc.github.io/activitynet-2016-cvprw/}{Project Link}}
    \end{cvitems}
}

\cventry
	{Master Thesis at Computer Vision Lab ETHZ}
	{Video Object Segmentation}
	{Z\"urich, Switzerland}
	{Jul. 2017 - Present}
	{
    \begin{cvitems}
    \item{
      The thesis explores interaction between the point regression techniques
      and the dense prediction techniques, specifically in the field of
      video object segmentation.}
    \item{
      Developed a web interface for interactive video object segmentation in
      real time. In addition can be used to visualize segmentation results.
      }
    \end{cvitems}
  }

\end{cventries}

\cvsection{Publications}

\begin{cvhonors}

  \cvhonor{A. Montes}{
A. Salvador, S. Pascual, and X. Giro-i-Nieto. Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks. In \emph{arXiv:1608.08128}
}{UPC, Barcelona}{2016}

\end{cvhonors}
% \bibliographystyle{ieee}
% \bibliographystyle{unsrtnat}
% \nobibliography{publications.bib}
% \bibentry{Montes2016}
% \begin{tabular}{L!{\VRule}R}
% 2016&\bibentry{Montes2016}\\
% \end{tabular}
% {
% \bibliographystyle{ieee}
% \bibliography{publications}
% }
